Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-15 paper/paper.Rmd
addig methods

>>>>

Seed dispersal kernels are functions used to describe the probability of a seed being dispersed or deposited at a specific distance away from its parent plant [@nathan_spatial_2000]. The resulting data from our three simulation models provided a dispersal distance for each simulated seed, and thus we used this information to describe the seed dispersal kernels for each model (null, individual, and family). Dispersal kernels in nature tend to be leptokurtic, with a peak near the origin and long tails, therefore kernel shape can be summarized by its kurtosis [@morales_effects_2006]. We quantified the dispersal kernels produced in our models by the sample statistics of mean and kurtosis to describe the overall shape and tail of distribution of seed dispersal distances. In addition to this, we also fit a Weibull distribution via maximum likelihood to obtain estimates of the shape and scale parameters in this distribution. A Weibull probability distribution is commonly used in dispersal ecology due to the flexible shape and ability to accommodate variability in the tail of the distribution.

In order to describe the seed dispersal kernels generated by our simulations under the three different models, we chose a Weibull distribution. This probability distribution is commonly used in dispersal ecology and has been shown to be flexible enough to accommodate variability in the tails and provide informative parameters associated to the mean dispersal distance and shape of the tail [@morales_effects_2006]. We fit the data associated to seed dispersal distances produced by each of the three models via Maximum Likelihood using the Weibull density function:
$$W(x) = \left(\frac{\kappa}{\nu}\right) \left(\frac{x}{\nu}\right)^{\kappa-1} exp[-(x/{\nu})^{\kappa}]$$

f(x) = (a/b) (x/b)^(a-1) exp(- (x/b)^a)
Where the shape parameter $\kappa$ is found to be the average seed dispersal distance from the data, and the scale parameter $\nu$ determines the tail of the distribution. Other variations of the Weibull density distribution describe the

```{r}
library(ggplot2)

ggplot(data = data.frame(x = c(0.1, 10)), aes(x)) +
  stat_function(fun = dweibull, n = 10, args = list(scale = 1, shape = 1), color = "red") +
  stat_function(fun = dweibull, n = 10, args = list(scale = 2, shape = 1), color = "blue") +
  stat_function(fun = dweibull, n = 10, args = list(scale = -2, shape = 1)) +
  ylab("")
